
\sectionTitle{Certificaciones}{\faMortarBoard}


%\begin{certification}
%	\certificationentry{January 2024} {asdasd}
%    {Visión por Computadora, Detección de Objetos, Estimación de Profundidad, Agricultura de Precisión}
%\end{certification}


\begin{certs}
  \cert
    {Marzo 2024} {Prepare for the Google Cloud Professional Machine Learning Engineer Certification}{Linkedin Learning}{}
    {}    {
      \begin{itemize}
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 1 Framing ML Problems.
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 2 Architecting ML Solution.
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 3 Designing Data Preparation and Processing Systems.
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 4 Developing ML Models.
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 5 Automating and Orchestrating ML Pipelines.
        \item Google Cloud Professional Machine Learning Engineer Cert Prep: 6 Monitoring, Optimizing, and Maintaining ML Solutions.
        \item Ver \href{https://www.linkedin.com/learning/certificates/64b7df30df810f9d340be254d70913a73bb7955c40502e8f248613ceb1cf5c4e}{\color{CadetBlue}{Certificado}}.
      \end{itemize}
    }
    {Data Processing, Machine Learning, Solution Architecture, Data Preparation, Artificial Intelligence (AI), Computer Vision, Google Cloud Platform (GCP), DevOps, MLOps}
    \emptySeparator
    \cert
    {Marzo 2024} {Career Essentials in Generative AI by Microsoft and LinkedIn}{Microsoft}{}
    {}    {
      \begin{itemize}
        \item What Is Generative AI?
        \item Generative AI: The Evolution of Thoughtful Online Search.
        \item Streamlining Your Work with Microsoft Copilot.
        \item Learning Microsoft 365 Copilot.
        \item Ethics in the Age of Generative AI.
        \item Introduction to Artificial Intelligence.
        \item Ver \href{https://www.linkedin.com/learning/certificates/a9341341fa8a79c18c53fdbf5266308236a238d77d7ad2b3cccda6cef2e2a67c}{\color{CadetBlue}{Certificado}}.
      \end{itemize}
    }
    {Computer Ethics, Productivity Improvement, Natural Language Processing (NLP), Generative AI, Search Engine Technology, Artificial Intelligence for Business, Microsoft 365, Artificial Intelligence (AI)} 
    \emptySeparator
    \cert
    {Abril 2024} {Prepare for the Microsoft Azure AI Fundamentals (AI-900) Certification}{Linkedin Learning}{}
    {}    {
      \begin{itemize}
        \item Microsoft Azure AI Fundamentals (AI-900) Exam Tips.
        \item Azure AI Fundamentals (AI-900) Cert Prep: 1 Conversational AI on Azure.
        \item Azure AI Fundamentals (AI-900) Cert Prep: 2 Principles of Machine Learning on Azure.
        \item Azure AI Fundamentals (AI-900) Cert Prep: 3 Computer Vision Workloads on Azure.
        \item Azure AI Fundamentals (AI-900) Cert Prep: 4 Natural Language Processing (NLP) Workloads on Azure.
        \item Ver \href{https://www.linkedin.com/learning/certificates/8724670360496820ace74307975a81ede24795b5f9f27d5c5000c1f155495735}{\color{CadetBlue}{Certificado}}.
      \end{itemize}
    }
    {Microsoft Azure, Machine Learning, Conversational AI, Artificial Intelligence (AI), Computer Vision, Natural Language Processing (NLP), Big Data}
    \emptySeparator
    \cert
    {Abril 2024} {Prepare for the AWS Certified Machine Learning - Specialty (MLS-C01) Exam}{Linkedin Learning}{}
    {}    {
      \begin{itemize}
        \item AWS Certified Machine Learning - Specialty (MLS-C01) Cert Prep: 1 Data Engineering.
        \item AWS Certified Machine Learning - Specialty (MLS-C01) Cert Prep: 2 Exploratory Data Analysis.
        \item AWS Certified Machine Learning - Specialty (MLS-C01) Cert Prep: 3 Modeling.
        \item AWS Certified Machine Learning - Specialty (MLS-C01) Cert Prep: 4 Machine Learning Implementation and Operations.
        \item Ver \href{https://www.linkedin.com/learning/certificates/5f7c2d8f4d0b5e254b7d03b4cc8ceab694ef17b4c567831e44cfdc0de9aaa378}{\color{CadetBlue}{Certificado}}.
      \end{itemize}
    }
    {Machine Learning, Artificial Intelligence (AI), Applied Machine Learning, Data Engineering, Exploratory Data Analysis, Data Modeling, Amazon Web Services (AWS), MLOps, Machine Learning}
    \emptySeparator
    \cert
    {Abril 2024} {Career Essentials in GitHub Professional Certificate}{GitHub}{}
    {}    {
      \begin{itemize}
        \item Practical GitHub Actions.
        \item Practical GitHub Project Management and Collaboration.
        \item Practical GitHub Copilot.
        \item Practical GitHub Code Search.
        \item Ver \href{https://www.linkedin.com/learning/certificates/c23b9c9dfaf002a5e1037568e5fa40d1facc167610ee06e1863539ed0ea498c1}{\color{CadetBlue}{Certificado}}.
      \end{itemize}
    }
    {GitHub, GitHub Copilot, Natural Language Processing (NLP), Project Management}     
\end{certs}